Validating Cell Tower Clustering for Mobility Prediction

### 2012-12-13 docs/paper589.tex
opencell

\section{Introduction}
\label{sec:intro}
\xxx{Talk about mobility prediction in mobile networks. Discuss some of the potential benefits -- some of them were discussed in the
ATT leap graph paper. Maybe do a little research on this.}

@@

\subsubsection{OpenCell}

>>>>

\section{Introduction}
\label{sec:intro}

@@

\subsubsection{OpenCellId and OpenBMap}

OpenCellId and OpenBmap are two open source projects with goal of providing researchers with a complete database of  cells with their locations. We use these two dataset for retrieving location information of cells
we have in MDC.
